Working with Code environments in texor

### 2023-07-23 supplement/code-env/code-example.tex
Edits to code example supplement

Hence \CRANpkg{texor} package uses the stream editor to search find and replace matching code environments to verbatim before pandoc touches it.

@@

\subsection{Verbatim Series}
While verbatim is naturally supported in pandoc,other extensions of verbatim environment
like boxedverbatim from moreverb package \citep{moreverb}.
% verbatim

@@

S series code environement is defined in Rjournal.sty file.

@@

\subsection{Example series}
Example series of code environment is defined in Rjournal.sty file.

@@

% Code in Figures
\section{Code in Figure Environments}
A small example of this is visble in \ref{code:example}

\begin{figure*}[htbp]
\begin{Sinput}
code_in_figure <- function() {
  if (pandoc_version >= 3) {
    print("Code in Figure Supported")
  }
  else {
    print("code in Figure not supported")
  }
}
\end{Sinput}
\caption{ Example Code inside Figure environment}
\label{code:example}
\end{figure*}
Pandoc v3 or greater \citep{pandoc} has a Figure object which allows non-image
figures to be treated like one.

% Code in Tables
\section{Code in Table Environments}
We can use code environments in a table using minipage environments.

>>>>

Hence, the \CRANpkg{texor} package uses a stream editor to search find and replace matching code environments to verbatim before pandoc touches it.

@@

\subsection{Verbatim Series}
While verbatim is naturally supported in pandoc,other extensions of verbatim environment
like boxedverbatim from moreverb package \citep{moreverb} falls back to normal verbatim.
% verbatim

@@

S series code environement is defined in Rjournal.sty file. Most of these are
extensions of verbatim environment and are represented as vanilla verbatim in HTML.

@@

\subsection{Example series}
Example series of code environment is defined in Rjournal.sty file. Examples are
extensions of verbatim environment and are represented as vanilla verbatim in HTML.

@@

% Code in Figures
\section{Code in Figure Environments}
A small example of this is visble in \ref{code:example}. This is a common practice
in Rnews articles as it used to add a boxed border around the code which looks 
attractive. However, in web articles there isn't much advantage to it.

\begin{figure}[htbp]
\begin{center}
\begin{verbatim}
code_in_figure <- function() {
  if (pandoc_version >= 3) {
    print("Code in Figure Supported")
  }
  else {
    print("code in Figure not supported")
  }
}
\end{verbatim}
\caption{ Example Code inside Figure environment}
\label{code:example}
\end{center}
\end{figure}

Pandoc v3 or greater \citep{pandoc} has a Figure object which allows non-image
figures to be treated like one. This is why \CRANpkg{texor} package requires atleast version 3
of pandoc.

% Code in Tables
\section{Code in Table Environments}
We can use code environments in a table using minipage environments. This is not
a common practice among LaTeX article authors, but a few articles had such complex
structures. So, as a example to demonstrate pandoc and \CRANpkg{texor} package's capabilities, 
I have included a few of them.
